Pillar 2 - Topic Modeling

### 2019-01-17 Pillar 2 - Topic Modeling.Rmd

## Course Level
```{r tf-idf course, out.height=8, out.width=16}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = Code) %>%
                                          group_by(facet) %>%
                                            filter(n >= 2) %>%
                                            top_n(10, tf_idf) %>%
                                          ungroup

@@

  data_gamma <- data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = mean(gamma)) %>%
    filter(gamma > 0.05) %>%
    ungroup %>%
    arrange(facet, desc(gamma))

@@

```{r}
# Bet Distribution
LDA_description_10 %>%
  prepare_data_LDA_beta %>%
  visualize_LDA_beta

@@

>>>>

## Course Level
```{r tf-idf course, out.height=8, out.width=16, cache = TRUE}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = Code) %>%
                                          group_by(facet) %>%
                                            filter(n >= 2) %>%
                                            top_n(10, tf_idf) %>%
                                          ungroup

@@

  data_gamma <- data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = sum(gamma)) %>%
    filter(gamma > 0.05) %>%
    ungroup %>%
    arrange(facet, desc(gamma))

@@

```{r, cache = TRUE}
# Bet Distribution
LDA_description_10 %>%
  prepare_data_LDA_beta %>%
  visualize_LDA_beta

@@

```{r}
visualize_LDA_all_level <- function(data, id_plot = "test"){

  data %>% 
    visualize_LDA(level = Course,
                  id_plot = paste(id_plot, "_course"))

  data %>% 
    visualize_LDA(level = Cluster,
                  id_plot = paste(id_plot, "_cluster"))

  data %>% 
    visualize_LDA(level = Concentration,
                  id_plot = paste(id_plot, "_concentration"))

```{r, cache = TRUE}
LDA_description_10 %>% visualize_LDA_all_level(id_plot = "description_k10")
LDA_description_17 %>% visualize_LDA_all_level(id_plot = "description_k17")
LDA_description_25 %>% visualize_LDA_all_level(id_plot = "description_k25")

LDA_overview_10 %>% visualize_LDA_all_level(id_plot = "overview_k10")
LDA_overview_17 %>% visualize_LDA_all_level(id_plot = "overview_k17")
LDA_overview_25 %>% visualize_LDA_all_level(id_plot = "overview_k25")

LDA_manual_10 %>% visualize_LDA_all_level(id_plot = "manual_k10")
LDA_manual_17 %>% visualize_LDA_all_level(id_plot = "manual_k17")
LDA_manual_25 %>% visualize_LDA_all_level(id_plot = "manual_k25")
```
